---
title: "Regression iiC"
author: "Keyon Hedayati"
date: "4/21/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, load_packages}
library(tidyverse)
library(caret)
library(coefplot)
library(rstanarm)


```


```{r, read_data_01}
df_all <- readr::read_csv("final_project_train.csv", col_names = TRUE)
```

Load the data and transform y

```{r, reg_01}
dfii <- df_all %>% 
  mutate(y = log(response)) %>% 
  select(region, customer, starts_with('x'), y)

```

Load models

```{r, load relevant models}

re_lm_cont_cust_add_region_X_splines <- readr::read_rds('bayes_cont_add_region_X_splines.rds')
re_lm_all_add <- readr::read_rds('lm_all_additive.rds')

```


**Spline 'winning' model**


```{r}
dfii %>% summary()
```


*Make the visualization grid*

A few of the important inputs appear to be "xs_06", "xw_03", and "customerK" seems like the easiest to predict customer based on  the coefficient plot in iiB.


```{r, viz grid for bayesian spline model}

colnames(dfii)
viz_grid <- expand.grid(xs_06 = seq(0, 1.9, length.out = 101),
                        xw_03 = seq(9, 125, length.out = 6),
                        xb_01 = median(dfii$xb_01),
                        xb_02 = median(dfii$xb_02),
                        xb_03 = median(dfii$xb_03),
                        xb_04 = median(dfii$xb_04),
                        xb_05 = median(dfii$xb_05),
                        xb_06 = median(dfii$xb_06),
                        xb_07 = median(dfii$xb_07),
                        xb_08 = median(dfii$xb_08),
                        xn_01 = median(dfii$xn_01),
                        xn_02 = median(dfii$xn_02),
                        xn_03 = median(dfii$xn_03),
                        xn_04 = median(dfii$xn_04),
                        xn_05 = median(dfii$xn_05),
                        xn_06 = median(dfii$xn_06),
                        xn_07 = median(dfii$xn_07),
                        xn_08 = median(dfii$xn_08),
                        xa_01 = median(dfii$xa_01),
                        xa_02 = median(dfii$xa_02),
                        xa_03 = median(dfii$xa_03),
                        xa_04 = median(dfii$xa_04),
                        xa_05 = median(dfii$xa_05),
                        xa_06 = median(dfii$xa_06),
                        xa_07 = median(dfii$xa_07),
                        xa_08 = median(dfii$xa_08),
                        xw_01 = median(dfii$xw_01),
                        xw_02 = median(dfii$xw_02),
                        #xw_03 = median(dfii$xw_03),
                        xs_01 = median(dfii$xs_01),
                        xs_02 = median(dfii$xs_02),
                        xs_03 = median(dfii$xs_03),
                        xs_04 = median(dfii$xs_04),
                        xs_05 = median(dfii$xs_05),
                        #xs_06 = median(dfii$xs_06),
                        region = "ZZ",
                        customer = "K",
                        KEEP.OUT.ATTRS = FALSE,
                        stringsAsFactors = FALSE) %>% 
  as.data.frame() %>% tibble::as_tibble()

```



```{r, prediction samples confidence}
pred_bayes <- posterior_linpred(re_lm_cont_cust_add_region_X_splines, newdata = viz_grid)

```


```{r, prediction for prediction interval}

pred_bayes_predict <- posterior_predict(re_lm_cont_cust_add_region_X_splines, newdata = viz_grid)

```
poster predict accounts for sigma, and RMSE

```{r, prediction interval table}
pred_bayes_pred <- pred_bayes_predict %>% 
  as.data.frame() %>% tibble::as_tibble() %>% 
  tibble::rowid_to_column("post_id") %>% 
  pivot_longer(!c("post_id"), names_to = 'pred_id') %>% 
  mutate(across(.cols = 'pred_id', .fns = as.numeric)) %>% 
  group_by(pred_id) %>% 
  summarise(num_post = n(),
            trend_avg = mean(value),
            trend_lwr = quantile(value, 0.05),
            trend_upr = quantile(value, 0.95)) %>% 
  ungroup() %>% 
  left_join(viz_grid %>% tibble::rowid_to_column("pred_id"),
            by = "pred_id") 



pred_bayes_pred %>% head()
```
*Prediction Interval Graphic*

```{r, baysian prediction interval graphic}
pred_bayes_pred %>% 
  ggplot(mapping = aes(x = xs_06)) +
  geom_ribbon(mapping = aes(ymin = trend_lwr,
                            ymax = trend_upr,
                            group = xw_03
                            ),
              alpha = 0.5) +
  
  geom_line(mapping = aes(y = trend_avg,
                          group = xw_03
                          #color = as.factor(xw_03)),
                          ),
            size = 1.) +
  facet_wrap(~xw_03, labeller = "label_both") +
  scale_fill_viridis_d("xw_03") +
  scale_color_viridis_d("xw_03") +
  labs(y = "mean trend") +
  theme_bw() +
  theme(legend.position = "top")
```

It appears the prediction points mostly fall very close to the trend line until you get to the edges of the inputs. They also follow a non-linear trend.


```{r, confidence interval table}
pred_bayes_conf <- pred_bayes %>% 
  as.data.frame() %>% tibble::as_tibble() %>% 
  tibble::rowid_to_column("post_id") %>% 
  pivot_longer(!c("post_id"), names_to = 'pred_id') %>% 
  mutate(across(.cols = 'pred_id', .fns = as.numeric)) %>% 
  group_by(pred_id) %>% 
  summarise(num_post = n(),
            trend_avg = mean(value),
            trend_lwr = quantile(value, 0.05),
            trend_upr = quantile(value, 0.95)) %>% 
  ungroup() %>% 
  left_join(viz_grid %>% tibble::rowid_to_column("pred_id"),
            by = "pred_id") 



pred_bayes_conf %>% head()
```

*Confidence Interval Graphics*

```{r, bayesian confidence interval}
pred_bayes_conf %>% 
  ggplot(mapping = aes(x = xs_06)) +
  geom_ribbon(mapping = aes(ymin = trend_lwr,
                            ymax = trend_upr,
                            group = xw_03
                            ),
              alpha = 0.5) +
  
  geom_line(mapping = aes(y = trend_avg,
                          group = xw_03
                          #color = as.factor(xw_03)),
                          ),
            size = 1.) +
  facet_wrap(~xw_03, labeller = "label_both") +
  scale_fill_viridis_d("xw_03") +
  scale_color_viridis_d("xw_03") +
  labs(y = "mean trend") +
  theme_bw() +
  theme(legend.position = "top")
```

The model is very confident around the middle of the inputs, with a narrow ribbon that grows wides at the edges of the input. As you can see, the trend is non-linear.

**All Additive Winning Model**

```{r, grid for all additive}
viz_grid_lm_all <- expand.grid(xb_04 = seq(-2, 5, length.out = 101),
                        xn_04 = seq(-4, 5, length.out = 6),
                        xb_01 = median(dfii$xb_01),
                        xb_02 = median(dfii$xb_02),
                        xb_03 = median(dfii$xb_03),
                        #xb_04 = median(dfii$xb_04),
                        xb_05 = median(dfii$xb_05),
                        xb_06 = median(dfii$xb_06),
                        xb_07 = median(dfii$xb_07),
                        xb_08 = median(dfii$xb_08),
                        xn_01 = median(dfii$xn_01),
                        xn_02 = median(dfii$xn_02),
                        xn_03 = median(dfii$xn_03),
                        #xn_04 = median(dfii$xn_04),
                        xn_05 = median(dfii$xn_05),
                        xn_06 = median(dfii$xn_06),
                        xn_07 = median(dfii$xn_07),
                        xn_08 = median(dfii$xn_08),
                        xa_01 = median(dfii$xa_01),
                        xa_02 = median(dfii$xa_02),
                        xa_03 = median(dfii$xa_03),
                        xa_04 = median(dfii$xa_04),
                        xa_05 = median(dfii$xa_05),
                        xa_06 = median(dfii$xa_06),
                        xa_07 = median(dfii$xa_07),
                        xa_08 = median(dfii$xa_08),
                        xw_01 = median(dfii$xw_01),
                        xw_02 = median(dfii$xw_02),
                        xw_03 = median(dfii$xw_03),
                        xs_01 = median(dfii$xs_01),
                        xs_02 = median(dfii$xs_02),
                        xs_03 = median(dfii$xs_03),
                        xs_04 = median(dfii$xs_04),
                        xs_05 = median(dfii$xs_05),
                        xs_06 = median(dfii$xs_06),
                        region = "ZZ",
                        customer = "K",
                        KEEP.OUT.ATTRS = FALSE,
                        stringsAsFactors = FALSE) %>% 
  as.data.frame() %>% tibble::as_tibble()

viz_grid_lm_all %>% glimpse()
```



```{r, prediction helper function}

tidy_predict <- function(mod, xnew)
{
  pred_df <- predict(mod, xnew, interval = "confidence") %>% 
    as.data.frame() %>% tibble::as_tibble() %>% 
    dplyr::select(pred = fit, ci_lwr = lwr, ci_upr = upr) %>% 
    bind_cols(predict(mod, xnew, interval = 'prediction') %>% 
                as.data.frame() %>% tibble::as_tibble() %>% 
                dplyr::select(pred_lwr = lwr, pred_upr = upr))
  
  xnew %>% bind_cols(pred_df)
}

```


```{r, make predictions for all additive}

pred_lm_all_add <- tidy_predict(re_lm_all_add, viz_grid_lm_all)
```


```{r, visualizations}

pred_lm_all_add %>% 
  ggplot(mapping = aes(x = xb_04)) +
  geom_ribbon(mapping = aes(ymin = pred_lwr, ymax = pred_upr),
              fill = 'orange') +
  geom_ribbon(mapping = aes(ymin = ci_lwr, ymax = ci_upr),
              fill = 'grey') +
  geom_line(mapping = aes(y = pred),
            color = 'black') +
  coord_cartesian(ylim = c(-7, 7)) +
  facet_wrap(~xn_04, labeller = "label_both") +
  theme_bw()

```

The trends are much more linear, and appear to have a negative slope as the inputs increase in value. Once again the confidence ribbon grows wider at the edges of the input showing less confidence at the edges.