---
title: "Classification iiiC"
author: "Keyon Hedayati"
date: "4/23/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, load_packages}
library(tidyverse)
library(caret)
library(coefplot)
library(rstanarm)


```


```{r, read_data_01}
df_all <- readr::read_csv("final_project_train.csv", col_names = TRUE)
```

Clean the data for classification:

```{r, class_03}
dfiiiA <- df_all %>% 
  mutate(y = ifelse(outcome == 'event', 1, 0)) %>% 
  select(region, customer, starts_with('x'), y)

```


Load models

```{r, load relevant models}

re_laplace_region_X_cont <- readr::read_rds('laplace_region_X_cont.rds')
re_laplace_all_add <- readr::read_rds('laplace_all_additive.rds')

```


```{r, df summary for grid later}
dfiiiA %>% summary()
```


```{r, viz grid for region}


viz_grid_region <- expand.grid(xw_02 = seq(min(dfiiiA$xw_02), max(dfiiiA$xw_02), length.out = 101),
                        xa_02 = seq(min(dfiiiA$xa_02), max(dfiiiA$xa_02), length.out = 5),
                        xb_01 = median(dfiiiA$xb_01),
                        xb_02 = median(dfiiiA$xb_02),
                        xb_03 = median(dfiiiA$xb_03),
                        xb_04 = median(dfiiiA$xb_04),
                        xb_05 = median(dfiiiA$xb_05),
                        xb_06 = median(dfiiiA$xb_06),
                        xb_07 = median(dfiiiA$xb_07),
                        xb_08 = median(dfiiiA$xb_08),
                        xn_01 = median(dfiiiA$xn_01),
                        xn_02 = median(dfiiiA$xn_02),
                        xn_03 = median(dfiiiA$xn_03),
                        xn_04 = median(dfiiiA$xn_04),
                        xn_05 = median(dfiiiA$xn_05),
                        xn_06 = median(dfiiiA$xn_06),
                        xn_07 = median(dfiiiA$xn_07),
                        xn_08 = median(dfiiiA$xn_08),
                        xa_01 = median(dfiiiA$xa_01),
                        #xa_02 = median(dfiiiA$xa_02),
                        xa_03 = median(dfiiiA$xa_03),
                        xa_04 = median(dfiiiA$xa_04),
                        xa_05 = median(dfiiiA$xa_05),
                        xa_06 = median(dfiiiA$xa_06),
                        xa_07 = median(dfiiiA$xa_07),
                        xa_08 = median(dfiiiA$xa_08),
                        xw_01 = median(dfiiiA$xw_01),
                        #xw_02 = median(dfiiiA$xw_02),
                        xw_03 = median(dfiiiA$xw_03),
                        xs_01 = median(dfiiiA$xs_01),
                        xs_02 = median(dfiiiA$xs_02),
                        xs_03 = median(dfiiiA$xs_03),
                        xs_04 = median(dfiiiA$xs_04),
                        xs_05 = median(dfiiiA$xs_05),
                        xs_06 = median(dfiiiA$xs_06),
                        region = median(dfiiiA$region),
                        customer = median(dfiiiA$customer),
                        KEEP.OUT.ATTRS = FALSE,
                        stringsAsFactors = FALSE) %>% 
  as.data.frame() %>% tibble::as_tibble()

viz_grid_region <- viz_grid_region %>% mutate(customer = factor(customer, levels=unique(dfiiiA$customer)), region = factor(region, levels=unique(dfiiiA$region)))

```



```{r, viz grid for glm all additive}


viz_grid <- expand.grid(xa_04 = seq(-2, 12, length.out = 101),
                        xn_08 = seq(-4, 5, length.out = 6),
                        xb_01 = median(dfiiiA$xb_01),
                        xb_02 = median(dfiiiA$xb_02),
                        xb_03 = median(dfiiiA$xb_03),
                        xb_04 = median(dfiiiA$xb_04),
                        xb_05 = median(dfiiiA$xb_05),
                        xb_06 = median(dfiiiA$xb_06),
                        xb_07 = median(dfiiiA$xb_07),
                        xb_08 = median(dfiiiA$xb_08),
                        xn_01 = median(dfiiiA$xn_01),
                        xn_02 = median(dfiiiA$xn_02),
                        xn_03 = median(dfiiiA$xn_03),
                        xn_04 = median(dfiiiA$xn_04),
                        xn_05 = median(dfiiiA$xn_05),
                        xn_06 = median(dfiiiA$xn_06),
                        xn_07 = median(dfiiiA$xn_07),
                        #xn_08 = median(dfiiiA$xn_08),
                        xa_01 = median(dfiiiA$xa_01),
                        xa_02 = median(dfiiiA$xa_02),
                        xa_03 = median(dfiiiA$xa_03),
                        #xa_04 = median(dfiiiA$xa_04),
                        xa_05 = median(dfiiiA$xa_05),
                        xa_06 = median(dfiiiA$xa_06),
                        xa_07 = median(dfiiiA$xa_07),
                        xa_08 = median(dfiiiA$xa_08),
                        xw_01 = median(dfiiiA$xw_01),
                        xw_02 = median(dfiiiA$xw_02),
                        xw_03 = median(dfiiiA$xw_03),
                        xs_01 = median(dfiiiA$xs_01),
                        xs_02 = median(dfiiiA$xs_02),
                        xs_03 = median(dfiiiA$xs_03),
                        xs_04 = median(dfiiiA$xs_04),
                        xs_05 = median(dfiiiA$xs_05),
                        xs_06 = median(dfiiiA$xs_06),
                        region = median(dfiiiA$region),
                        customer = median(dfiiiA$customer),
                        KEEP.OUT.ATTRS = FALSE,
                        stringsAsFactors = FALSE) %>% 
  as.data.frame() %>% tibble::as_tibble()

viz_grid %>% glimpse()
```


```{r, viz_grid fix for model.matrix}
viz_grid_test <- viz_grid %>% mutate(customer = factor(customer, levels=unique(dfiiiA$customer)), region = factor(region, levels=unique(dfiiiA$region)))
viz_grid_test %>% glimpse()
```


Function below used to generate samples based on our laplace objects.

```{r, generate samples}
generate_glm_post_samples <- function(mvn_result, num_samples)
{
  # specify the number of unknown beta parameters
  length_beta <- length(mvn_result$mode)
  
  # generate the random samples
  beta_samples <- MASS::mvrnorm(n = num_samples, 
                                mu = mvn_result$mode, 
                                Sigma = mvn_result$var_matrix)
  
  # change the data type and name
  beta_samples %>% 
    as.data.frame() %>% tibble::as_tibble() %>% 
    purrr::set_names(sprintf("beta_%02d", (1:length_beta) - 1))
}
```

The below code will help identify the mean trend, and posterior predictions

```{r, mean trend and predictions}

post_logistic_pred_samples <- function(Xnew, Bmat)
{
  # calculate the linear predictor at all prediction points and posterior samples
  eta_mat <- Xnew %*% t(Bmat)
  
  # calculate the event probability
  mu_mat <- boot::inv.logit(eta_mat)
  
  # book keeping
  list(eta_mat = eta_mat, mu_mat = mu_mat)
}

```


This will handle the bookkeeping and gives us the quantiles and will help visualize.

```{r, bookkeeping}

summarize_logistic_pred_from_laplace <- function(mvn_result, Xtest, num_samples)
{
  # generate posterior samples of the beta parameters
  betas <- generate_glm_post_samples(mvn_result, num_samples)
  
  # data type conversion
  betas <- as.matrix(betas)
  
  # make posterior predictions on the test set
  pred_test <- post_logistic_pred_samples(Xtest, betas)
  
  # calculate summary statistics on the posterior predicted probability
  # summarize over the posterior samples
  
  # posterior mean, should you summarize along rows (rowMeans) or 
  # summarize down columns (colMeans) ???
  mu_avg <- rowMeans(pred_test$mu_mat)
  
  # posterior quantiles
  mu_q05 <- apply(pred_test$mu_mat, 1, stats::quantile, probs = 0.05)
  mu_q95 <- apply(pred_test$mu_mat, 1, stats::quantile, probs = 0.95)
  
  # book keeping
  tibble::tibble(
    mu_avg = mu_avg,
    mu_q05 = mu_q05,
    mu_q95 = mu_q95
  ) %>% 
    tibble::rowid_to_column("pred_id")
}
```


```{r, test design matric for all additive}

Xmat_additive <- model.matrix( ~ (.), data = viz_grid_test)

```


```{r, all additive prediction summary}

post_pred_summary_linear <- summarize_logistic_pred_from_laplace(re_laplace_all_add, 
                                                                 Xmat_additive, 
                                                                 2500)
post_pred_summary_linear %>% glimpse()
```


```{r, all additive baysian}
post_pred_summary_linear %>% 
  mutate(type = "All Additive") %>% 
  left_join(viz_grid_test %>% tibble::rowid_to_column("pred_id"),
            by = "pred_id") %>% 
  ggplot(mapping = aes(x = xa_04)) +
  geom_ribbon(mapping = aes(ymin = mu_q05,
                            ymax = mu_q95,
                            group = type),
              fill = "steelblue", alpha = 0.5) +
  geom_line(mapping = aes(y = mu_avg,
                          group = type),
            color = "navyblue", size = 1.15) +
  #geom_point(mapping = aes(y = y),
  #           size = 2.5, alpha = 0.2) +
  facet_grid( . ~ xn_08) +
  labs(y = "y or event probability") +
  theme_bw()
```

It appears from the above graphic that there is only a slight change in event prob as the inputs increase. On top of that there is a very high amount of uncertainty. This makes me believe that the features are potentially not as important as initially suspected.

```{r, test design matrix for region}

Xmat_region <- model.matrix( ~ (region) * (. -customer), data = viz_grid_region)

```


```{r, pred for spline model}

post_pred_summary_region <- summarize_logistic_pred_from_laplace(re_laplace_region_X_cont, 
                                                                 Xmat_region, 
                                                                 2500)
post_pred_summary_region %>% glimpse()
```


```{r}
post_pred_summary_region %>% 
  left_join(dfiiiA %>% tibble::rowid_to_column("pred_id"),
            by = "pred_id") %>% 
  ggplot(mapping = aes(x = xw_02)) +
  geom_ribbon(mapping = aes(ymin = mu_q05,
                            ymax = mu_q95
                            ),
              fill = "steelblue", alpha = 0.5) +
  geom_line(mapping = aes(y = mu_avg
                          ),
            color = "navyblue", size = 1.15) +
  geom_point(mapping = aes(y = y),
             size = 2.5, alpha = 0.2) +
  labs(y = "y or event probability") +
  theme_bw()
```

I either did something wrong, or we are very uncertain about the event probability with the region interaction with continous. Which may mean that many of the features don't actually help.